%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This is a modified ONE COLUMN version of
% the following template:
% 
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume}
\RequirePackage{fontawesome}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Jose M.}{Ballesteros}
{\href{https://github.com/josemballes99}{\faGithubSquare\ \, josemballes99} \\
\href{mailto: test@test.com} \faEnvelope{ \,  any@anyemail.com} | \href{https://www.linkedin.com/in/josemballes/}{\faLinkedinSquare \, josemballes}  | {\faMobile \, (123) 456-7899} 
}

%\href{https://github.com/josemballes99}{\faGithubSquare\ \, josemballes99}

% OPTIONAL
\begin{center}
\huge\color{subheadings}\bf{SOFTWARE ENGINEER}
\end{center}

\section{Employment}

\runsubsection{Cox Automotive}
\descript{| Software Engineer}
\location{March 2021 - Present | Mississauga, ON}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Built all the required resources needed for a scheduled process utilizing AWS cloud services AuroraDB, SQS and Lambda. As well as delivering the data through a public facing C\# (.NET 5) API,  using a secure authentication process with AWS services API Gateway and Cognito
\item Created and supported the release of a new RESTful API utilizing the latest .NET as part of the company's cloud migration plans for a core business product, therefore improving the product's efficiency and the delivery speed for future release cycles.
\item Always working on the development and release for new features towards the company's flagship products.
\item Work under an industry standard Agile environment prioritizing product delivery and customer satisfaction, by utilizing common methodologies such as sprint planning, scrum poker and backlog refinement.
\item Execute project builds using Jenkins, as part of the company's desired CI/CD pipeline, while gaining a better understanding on DevOps and Automation pipelines in general. 
\end{tightemize}
\sectionsep

\runsubsection{Cox Automotive}
\descript{| Software Engineering Intern }
\location{September 2018 - December 2019 | Mississauga, ON}
%\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Took on and accomplished the individual challenge of migrating one of the company's integral admin application from AngularJS to Angular, as well as migrating the back-end APIs and all it's dependencies from .NET framework (4.6) into latest .NET Core.
\item Refactored the entire Angular client app for one of our vital products by using techniques to simplify and reuse components, eliminating \textasciitilde1000 lines of redundant code for cleaner legibility and overall performance.
\item Introduced modern software documentation practices by creating an entire wiki for one of our application's Github page including, a general overview, technical outlines, and engineering diagrams.
\item Integrated a 3rd-Party WYSIWYG editor into one of our staple products, taking into consideration client requirements and company security compliances.
\end{tightemize}
\sectionsep

\runsubsection{Wyzelink Systems Inc.}
\descript{| QA \& Support Engineer (Co-Op) }
\location{May 2018 - August 2018 | Mississauga, ON}
%\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Developed scripts and automation tools to improve the company's testing efficiency.
\item Wrote detailed procedures on defect findings on Github, thereby assisting the developers with reduced debugging and repairing time.
\item Worked directly with the startup's CEO to create a structured method for handling customer support emails, tickets and calls.
%\item Ensured quality for the entire system including server-side, customer frontend and device firmware.
%\item Collaborated with a team to update outdated company documents such as website, user guides and presentations.
\end{tightemize}
\sectionsep

\section{Education}
\runsubsection{McMaster University}
\descript{| B.Eng in Software Engineering}
\location{April 2020 | Hamilton, ON} %\textbullet{} Cum. GPA: N/A}
\sectionsep

%\section{Projects}
%\runsubsection{Cornell Robot Learning Lab}
%\descript{| Head Undergrad Research}
%\location{Jan 2014 ? Present | Ithaca, NY}
%Worked with \textbf{\href{http://www.cs.cornell.edu/~ashesh/}{Ashesh Jain}} and \textbf{\href{http://www.cs.cornell.edu/~asaxena/}{Prof Ashutosh Saxena}} to create \textbf{PlanIt}, a tool which  learns from large scale user preference feedback to plan robot trajectories in human environments.  Publication submitted.
%\sectionsep

\section{Skills}
\begin{minipage}[t]{.6\textwidth}
\subsection{Languages}
\location{Languages}
C\# \textbullet{}  Python \textbullet{} Java \textbullet{} SQL \textbullet{} JavaScript \textbullet{} TypeScript \textbullet{} HTML \textbullet{} CSS \textbullet{} Bash \textbullet{} Matlab \textbullet{} \LaTeX\ \\ 
\location{Frameworks}
Angular \textbullet{} React \textbullet{} .NET Core \textbullet{} Bootstrap \textbullet{} Flask \\
\location{Tools}
Git \textbullet{} AWS \textbullet{} Jenkins \textbullet{}  node.js \textbullet{} npm \textbullet{} Google Cloud (GCP)
\sectionsep
\end{minipage}
\hfill
\begin{minipage}[t]{.35\textwidth}
\subsection{Technologies}
\location{Software} Visual Studio, Android Studio, Unity \\
\location{Databases} Oracle, MongoDB, MySQL, IBM DB2\\
\location{OSs} Mac, Windows, Linux\\
\end{minipage}

%\section{Hackathons}
%\runsubsection{McMaster University}
%\descript{| Deltahacks}
%\location{January 2016 - Present | Hamilton, ON}
%\begin{tightemize}
%\item Created a GoogleChrome extension that allows for quick lookup of highlighted words through multiple APIs, such as Wikipedia, Wolframalpha, Dictionary.
%\item In a team, created the UI for a ArcelorMittal Dofasco alert tracking system using the Django framework.
%\item Worked with a team to create a problem solving game for children on Android Studio to assist them into learning the basics of logic.
%\end{tightemize}
%\sectionsep


\end{document}  \documentclass[]{article}